Oregon_Wildfire_reduced

### 2017-02-15 r_scripts/oregon_clean.rmd
Update oregon_clean.rmd
reduced data set r markdown...needs improving

---
title: "Oregon_Wildfire_Claim"
author: "Jingyang Liu"
date: "February 14, 2017"
output: html_document
---

@@

```{r, echo = F}
library(dplyr)
library(data.table)

# import data ------------------------------------------------------------------
read_path <- paste0("../data/gan_episodes_of_care.txt")

start_time <- Sys.time()
oregon_full <- fread(read_path, sep = "|", showProgress = T) # not change class
stop_time <-  Sys.time() - start_time 
# time it took
stop_time # 7.771713 mins

# Explore data structure
summary(as.factor(oregon_full$clmstatus))

# Clean data
oregon_full_df <- oregon_full %>%
  # filter non-missing value of gender, race 
  filter (gender!='U') %>%
  filter (is.na(race)==F)

# filter dx1, no ndc
oregon_full_dx1 <- oregon_full_df %>%
  filter (dx1!='*NULL*')

# filter ndc, no dx1
oregon_full_ndc <- oregon_full_df %>%
  filter (ndc!="")

fwrite(oregon_full_dx1, "../data/oregon_full_dx1.csv")
fwrite(oregon_full_ndc, "../data/oregon_full_ndc.csv")

write_path1 <- paste0('../data/','oregon_full_dx1.csv')
write_csv(oregon_full_dx1, write_path1)

write_path2 <- paste0('../data/','oregon_full_ndc.csv')
write_csv(oregon_full_ndc, write_path2)

@@

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "Oregon_Wildfire_reduced"
author: "Jingyang Liu"
date: "February 15, 2017"
output: html_document
---

@@

```{r}
library(dplyr)
library(data.table)

# import data ------------------------------------------------------------------
# Read in first 2000000 lines for exploration.

# read_path <- paste0("./data/gan_episodes_of_care.txt")
# oregon_df <- fread(read_path, sep = "|", nrows = 200000, showProgress = T)
# fwrite(oregon_df, "./data/oregon_epis_care_reduced.csv")

# I wrote a reduced dataframe of 2000,000 rows to get an idea of data structure

# import the reduced dataframe
start_time <- Sys.time()

oregon_df <- fread("./data/oregon_epis_care_reduced.csv", sep = ",")

stop_time <-  Sys.time() - start_time

# time it took
stop_time # 15.83603 secs

@@

#  The variable "clmstatus" is ..... It is a binary

```{r claim status}

# Explore data structure, try like clmstatus
summary(oregon_df)
summary(as.factor(oregon_df$clmstatus))

## Clean data

```{r }
# Clean data, 76986701 left (maybe later)
#oregon_full_df <- oregon_full %>%
  # filter non-missing value of year of birth, gender, race, STATE
#  filter (is.na(yob)==F) %>%
#  filter (gender!='U') %>%
#  filter (is.na(race)==F) %>%
#  filter (STATE!='')

# Explore no dx1 and no ndc, see if the dx2 or other reasons, 1042984 obs
# oregon_full_miss <- oregon_full %>%
#  filter (dx1=='*NULL*') %>%
#  filter (ndc=="")

# fwrite(oregon_full_miss, "../data/oregon_full_miss.csv")

# read_path1 <- paste0("./data/oregon_full_miss.csv")
# oregon_miss <- fread(read_path1, sep = ",")

# oregon_miss_df <- oregon_miss %>%
#   filter (dx2!='*NULL*') # 981 obs

# filter dx1, no ndc, 52490460
# oregon_full_dx1 <- oregon_full_df %>%
#   filter (dx1!='*NULL*')

# filter ndc, no dx1, 23453379
# oregon_full_ndc <- oregon_full_df %>%
#  filter (ndc!="")

# fwrite(oregon_full_dx1, "../data/oregon_full_dx1.csv")
# fwrite(oregon_full_ndc, "../data/oregon_full_ndc.csv")
